### 2016-10-19 methodsPaper/tex/results.tex

Adapting ITHIM's methods to the R platform enables the rapid and thorough assessment of parameter influence within the model. Another important improvement enabled by the shift to a more computationaly robust platform was to examine methodological assumptions of former implementations. One critical assumption invovles the approximation of _____ used to calculate the attirbutable fraction (see Figure \ref{fig:overview}). Previous implementations used quitiles to approximate this value, essentailly the area under the ___????___ curve. We improved upon those methods to use percentiles or 100 points to estimate the same values. We find our estimates to be much more stable and reliable at all values of active travel and non-travel activity parameters.

>>>>

Adapting ITHIM's methods to the R platform enables the rapid and
thorough assessment of parameter influence within the model. Another
important improvement enabled by the shift to a more computationaly
robust platform was to examine methodological assumptions of former
implementations. One critical assumption invovles the approximation of
??? used to calculate the attirbutable fraction (see
Figure \ref{fig:overview}). Previous implementations used quitiles to
approximate this value, essentailly the area under the ???? curve. We
improved upon those methods to use percentiles or 100 points to
estimate the same values. We find our estimates to be much more stable
and reliable at all values of active travel and non-travel activity
parameters.
